True versus apparent shapes of astrophysical bow shocks

### 2016-06-15 papers/Paper1/sec-projection.tex
Include POS projection figure in section 3
And brief discussion in text

Consider body-frame cartesian coordinates $(x,y,z)$, where \(x\) is
the symmetry axis, and spherical polar coordinates
\((R, \theta, \phi)\), where \(\theta\) is the polar angle and
\(\phi\) the azimuthal angle.  Since the surface is cylindrically
symmetric, it is can be specified as $R = R(\theta)$, so that
cartesian coordinates on the surface are:
\begin{equation}
\left(\begin{array}{c}
x \\ y \\ z
\end{array}
\right) = R(\theta)\left(\begin{array}{c}
\cos\theta \\
\sin\theta\cos\phi \\
\sin\theta\sin\phi
\end{array}\right).
\end{equation} 
Suppose that the viewing direction makes an angle \(i\) with the \(z\)
axis, so that we can define observer-frame coordinates
\((x', y', z')\), which are given by the rotating the body-frame
coordinates:
\begin{equation}
\left(\begin{array}{c}
x' \\ y' \\ z'
\end{array}
\right) = \left(\begin{array}{c}
x\cos i - z\sin i\\
y \\
z\cos i + x\sin i
\end{array}\right).
\label{eq:Trans}
\end{equation} 
In what follows, all quantities in the observer's frame are denoted by
attaching a prime to the equivalent quantity in the body frame.  The
coordinates \(x'\) and \(y'\) are in the plane of the sky, with \(x'\)
being the projected symmetry axis of the surface, while the line of
sight lies along \(-z'\).  The inclination angle \(i\) is defined so
that \(i = 0^\circ\) when the surface is viewed perpendicular to its
axis (\textit{side on}) and \(i = 90^\circ\) when it is viewed along
its axis (\textit{end on}).

>>>>

Consider body-frame cartesian coordinates $(x,y,z)$, where \(x\) is
the symmetry axis, and spherical polar coordinates
\((R, \theta, \phi)\), where \(\theta\) is the polar angle and
\(\phi\) the azimuthal angle.  Since the surface is cylindrically
symmetric, it is can be specified as $R = R(\theta)$, so that
cartesian coordinates on the surface are:
\begin{equation}
\left(\begin{array}{c}
x \\ y \\ z
\end{array}
\right) = R(\theta)\left(\begin{array}{c}
\cos\theta \\
\sin\theta\cos\phi \\
\sin\theta\sin\phi
\end{array}\right).
\end{equation} 
Suppose that the viewing direction makes an angle \(i\) with the \(z\)
axis, so that we can define observer-frame coordinates
\((x', y', z')\), which are given by the rotating the body-frame
coordinates:
\begin{equation}
\left(\begin{array}{c}
x' \\ y' \\ z'
\end{array}
\right) = \left(\begin{array}{c}
x\cos i - z\sin i\\
y \\
z\cos i + x\sin i
\end{array}\right).
\label{eq:Trans}
\end{equation} 
The relationship between the two frames is illustrated in
Figure~\ref{fig:projection-pos}.  All quantities in the observer's
frame are denoted by attaching a prime to the equivalent quantity in
the body frame.  The celestial coordinates on the ``plane of the sky''
are given by \((x', y')\) with \(x'\) being the projected symmetry
axis of the surface, while the line of sight lies along \(-z'\).  The
inclination angle \(i\) is defined so that \(i = 0^\circ\) when the
surface is viewed perpendicular to its axis (\textit{side on}) and
\(i = 90^\circ\) when it is viewed along its axis (\textit{end on}).

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/projection-pos}
  \caption{Relationship between body frame (unprimed coordinates) and
    observer frame (primed coordinates).}
  \label{fig:projection-pos}
\end{figure}
